Tutorial_4

### 2024-12-16 Tutorial_4.Rmd
updated tutorial 4. added sim data loading from the OSF.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=F)
```

@@

```{r load-pkg, results='hide'}
pkg <- c("cmdstanr", "standist", "tidyverse", "RColorBrewer", "patchwork", 
         "brms", "tidybayes", "bayesplot", "future", "parallel", "VGAM", "faux",
         "rstan")

@@

For Lisa's faux package, see here: [https://debruine.github.io/faux/](https://debruine.github.io/faux/).
The vignettes provided by the faux package are particularly helpful and worth following before you take a deep dive in the below code. 
There is also an associated [journal article](https://doi.org/10.1177/2515245920965119), which is worth reading.

@@

For simplicity, we use these normal(0,2) priors for the mean per condition.
However, if we were doing this for real, we would probably choose different priors that are similar to ones that were discussed in Tutorial_2a as well as in Supplmentary Materials.

@@

read in the file, if it is already computed

```{r load-sim1, eval=F}
sx1 <- read_csv("Tutorial_4_planning/data/sim1/sim1_data.csv") %>%
  mutate(exp=factor(exp),
         subj_n=factor(subj_n),
         rep_n=factor(rep_n),
         b6c = factor(b6c,
                      levels = c("-1.94", "-1.5", "-0.67"),
                      labels = c("25%", "50%", "75%")),
         subj=factor(subj),
         bin=factor(bin))
sx1
```

@@

```{r exp-summary-sim1, eval=F}
sx1_exp <- sx1 %>% 
  group_by(exp, subj_n, rep_n, b6c, condition, bin) %>% 
  summarise(exp_mean_outcome = mean(mean_outcome, na.rm = TRUE),
            exp_mean_sum=mean(sum, na.rm = TRUE),
            exp_sum=sum(sum),
            n = length(unique(subj)), 
            sd=sd(mean_outcome, na.rm = TRUE),
            sem = (sd/sqrt(length(unique(subj)))),
            .groups = "drop")
sx1_exp
```

@@

```{r sim-summary-sim1, eval=F}
sx1_sim <- sx1_exp %>% 
  group_by(subj_n, rep_n, b6c, condition, bin) %>% 
  summarise(sim_mean_outcome = mean(exp_mean_outcome, na.rm = TRUE),
            sim_mean_sum = mean(exp_mean_sum, na.rm = TRUE),
            sim_sum = mean(exp_sum, na.rm = TRUE),
            n = length(unique(exp)), 
            sd=sd(exp_mean_outcome, na.rm = TRUE),
            sem = (sd/sqrt(length(unique(exp)))),
            .groups = "drop")
sx1_sim
```

@@

```{r sim1-violin, eval=F}
p9.1 <- ggplot(sx1_sim, 
                aes(x = bin, y = sim_mean_outcome, 
                    colour = condition)) +
  geom_jitter(data=sx1_exp, aes(y = exp_mean_outcome),
              alpha=0.5, width = 0.1, height = 0) +
  geom_line(aes(group = condition)) + 
  geom_point(size=2, colour = "black") +
  geom_errorbar(aes(ymin = sim_mean_outcome-sem*1.96, ymax = sim_mean_outcome+sem*1.96),
                width=.2, colour = "black") +
  scale_colour_brewer(palette = "Dark2") +
  scale_y_continuous(limits = c(0,1), breaks = seq(0,1,0.25)) +
  labs(x="time bin",
       y="outcome") + 
  facet_grid(fct_rev(rep_n)~b6c)
p9.1

@@

read in the file, if it is already computed

```{r load-sim2}
sx2 <- read_csv("Tutorial_4_planning/data/sim2/sim2_data.csv") %>%
  mutate(exp=factor(exp),
         subj_n=factor(subj_n),
         rep_n=factor(rep_n),
         b6c = factor(b6c,
                      levels = c("-1.5", "-1.25", "-0.9"),
                      labels = c("50%", "60%", "70%")),
         subj=factor(subj),
         bin=factor(bin))
sx2
```

@@

```{r}
p12.1 <- (p10.4 | p11.6) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(axes = 'collect')
p12.1

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=T)
```

@@

```{r load-pkg, results='hide'}
pkg <- c("cmdstanr", "standist", "tidyverse", "RColorBrewer", "patchwork", 
         "brms", "tidybayes", "bayesplot", "future", "parallel", "VGAM", "faux",
         "rstan", "osfr")

@@

For Lisa's faux package, see here: [https://debruine.github.io/faux/](https://debruine.github.io/faux/).
The vignettes provided by the faux package are particularly helpful and worth following before you take a deep dive into the below code. 
There is also an associated [journal article](https://doi.org/10.1177/2515245920965119), which is worth reading.

@@

For simplicity, we use these normal(0,2) priors for the mean per condition.
However, if we were doing this for real, we would probably choose different priors that are similar to ones that were discussed in Tutorial_2a, as well as in Supplementary Materials.

@@

read in the file, if it is already computed.

If necessary, read it from the OSF to start with (because it is a large file). 
This step is only required to be done once.
After that, the file will be in your local directory and you can skip this chunk in the future.
To do so, set eval=TRUE in the chunk below, then re-set to FALSE once the data have been downloaded.

```{r load-osf-sim1, eval=F}
## create a relevant folder
dir.create("Tutorial_4_planning/data/sim1/")

## read in the data from the OSF and store it in a relevant folder
osf_sim1_data <-
  # retrieve the OSF (main) project
  osf_retrieve_node("3dbcs") %>% ## this is just one project picked at random
  # list files in this repository - there must be a more efficient way than this...
  osf_ls_files(pattern = "Tutorial_4_planning") %>%
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "sim1") %>%
  osf_ls_files(pattern = "sim1_data") %>%
  osf_download(path = "./Tutorial_4_planning/data/sim1/")
```

read the file from a local folder

```{r load-sim1, eval=T}
sx1 <- read_csv("Tutorial_4_planning/data/sim1/sim1_data.csv") %>%
  mutate(exp=factor(exp),
         subj_n=factor(subj_n),
         rep_n=factor(rep_n),
         b6c = factor(b6c,
                      levels = c("-1.94", "-1.5", "-0.67"),
                      labels = c("25%", "50%", "75%")),
         subj=factor(subj),
         bin=factor(bin))
sx1
```

@@

```{r exp-summary-sim1, eval=T}
sx1_exp <- sx1 %>% 
  group_by(exp, subj_n, rep_n, b6c, condition, bin) %>% 
  summarise(exp_mean_outcome = mean(mean_outcome, na.rm = TRUE),
            exp_mean_sum=mean(sum, na.rm = TRUE),
            exp_sum=sum(sum),
            n = length(unique(subj)), 
            sd=sd(mean_outcome, na.rm = TRUE),
            sem = (sd/sqrt(length(unique(subj)))),
            .groups = "drop")
sx1_exp
```

@@

```{r sim-summary-sim1, eval=T}
sx1_sim <- sx1_exp %>% 
  group_by(subj_n, rep_n, b6c, condition, bin) %>% 
  summarise(sim_mean_outcome = mean(exp_mean_outcome, na.rm = TRUE),
            sim_mean_sum = mean(exp_mean_sum, na.rm = TRUE),
            sim_sum = mean(exp_sum, na.rm = TRUE),
            n = length(unique(exp)), 
            sd=sd(exp_mean_outcome, na.rm = TRUE),
            sem = (sd/sqrt(length(unique(exp)))),
            .groups = "drop")
sx1_sim
```

@@

```{r sim1-violin, eval=T}
p9.1 <- ggplot(sx1_sim, 
                aes(x = bin, y = sim_mean_outcome, 
                    colour = condition)) +
  geom_jitter(data=sx1_exp, aes(y = exp_mean_outcome),
              alpha=0.5, width = 0.1, height = 0) +
  geom_line(aes(group = condition)) + 
  geom_point(size=2, colour = "black") +
  geom_errorbar(aes(ymin = sim_mean_outcome-sem*1.96, ymax = sim_mean_outcome+sem*1.96),
                width=.2, colour = "black") +
  scale_colour_brewer(palette = "Dark2") +
  scale_y_continuous(limits = c(0,1), breaks = seq(0,1,0.25)) +
  labs(x="time bin",
       y="outcome") + 
  facet_grid(fct_rev(rep_n)~b6c)
p9.1

@@

read in the file, if it is already computed.

If necessary, read it from the OSF to start with (because it is a large file). 
This step is only required to be done once.
After that, the file will be in your local directory and you can skip this chunk in the future.
To do so, set eval=TRUE in the chunk below, then re-set to FALSE once the data have been downloaded.

```{r load-osf-sim2, eval=F}
## create a relevant folder
dir.create("Tutorial_4_planning/data/sim2/")

## read in the data from the OSF and store it in a relevant folder
osf_sim2_data <-
  # retrieve the OSF (main) project
  osf_retrieve_node("3dbcs") %>% ## this is just one project picked at random
  # list files in this repository - there must be a more efficient way than this...
  osf_ls_files(pattern = "Tutorial_4_planning") %>%
  osf_ls_files(pattern = "data") %>%
  osf_ls_files(pattern = "sim2") %>%
  osf_ls_files(pattern = "sim2_data") %>%
  osf_download(path = "./Tutorial_4_planning/data/sim2/")
```

read the file from a local folder

```{r load-sim2, eval=T}
sx2 <- read_csv("Tutorial_4_planning/data/sim2/sim2_data.csv") %>%
  mutate(exp=factor(exp),
         subj_n=factor(subj_n),
         rep_n=factor(rep_n),
         b6c = factor(b6c,
                      levels = c("-1.5", "-1.25", "-0.9"),
                      labels = c("50%", "60%", "70%")),
         subj=factor(subj),
         bin=factor(bin))
sx2
```

@@

```{r sim1-sim2-power-plot}
p12.1 <- (p10.4 | p11.6) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(axes = 'collect')
p12.1
